### 2015-06-17 Dissertation/abstract.tex
Forgot to update abstract to remove "wall clock time"

Across seven problems, each tested using on average 18 problem sizes, P3 outperformed
all five advanced comparison algorithms. This improvement includes requiring fewer evaluations
and less wall clock seconds to find the global optimum and better fitness when using
the same number of evaluations. Using both algorithm analysis and comparison we show P3's
effectiveness is due to its ability to properly maintain, add, and exploit diversity.

>>>>

Across seven problems, each tested using on average 18 problem sizes, P3 outperformed
all five advanced comparison algorithms. This improvement includes requiring fewer evaluations
to find the global optimum and better fitness when using
the same number of evaluations. Using both algorithm analysis and comparison we show P3's
effectiveness is due to its ability to properly maintain, add, and exploit diversity.
